
---
title: "Shiny Application and Reproducible Pitch"
author: "Emilio Garcia"
date: "2/04/2021"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Your Shiny Application

1. Write a shiny application with associated supporting documentation.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github
5. Some form of input (widget: textbox, radio button, ...)
6. Some operation on the ui input in sever.R
7. Some reactive output displayed as a result of server calculations.
8. The documentation should be at the Shiny website itself.

```{r}
```

## Data Descriptive

```{r, fig.align='center', message = FALSE}

library(datasets)
library(caret)
library(quantmod)
library(dplyr)

from.dat <- as.Date("01/01/17", format="%m/%d/%y")

to.dat <- as.Date("01/01/21", format="%m/%d/%y")

getSymbols(c("GOOG","AAPL","FB","F","BA", "C"), src="yahoo", from = from.dat, to = to.dat)

GOOG <- GOOG %>% as.data.frame()
AAPL <- AAPL %>% as.data.frame()
FB <- FB %>% as.data.frame()
BA <- BA %>% as.data.frame()
C <- C %>% as.data.frame()
  
fecha <- rownames(FB) 
  
stocks <- data.frame(Fecha=fecha[-1],AAPL=diff(log(AAPL$AAPL.Close),1),
                       GOOG=diff(log(GOOG$GOOG.Close),1),
                       FB=diff(log(FB$FB.Close),1),
                       BA=diff(log(BA$BA.Close),1),
                       C=diff(log(C$C.Close),1))

stocks4corr <- stocks %>% select("AAPL","GOOG","FB","BA","C")

tail(stocks4corr,5)
```

## Instruction for use

1. Select the sample size of interest
2. Select the stocks 
3. The result shows the correlation among the chosen stocks

```{r}
```

## Stock Correlation Matrix

```{r, fig.align='center', message = FALSE, warning=FALSE}

stocks4corr <- stocks %>% select("AAPL","GOOG","FB","BA","C") 

round(cor(tail(stocks4corr[,c(TRUE,TRUE,TRUE,TRUE,TRUE)],3)),2)

```
